Dismal Code: Studying the Evolution of Security Bugs

### 2013-03-11 docs/evol.tex
added evol files; moved data in data directory
updated figure
some rearrangements, new citations

One of the most common approaches to identify security bugs is
{\it static analysis}~\cite{CW07}. This kind of analysis involves the
inspection of the program's source or object code without executing
it. For our research we used {\it FindBugs},\footnote{\url{http://findbugs.sourceforge.net/}}
a static analysis tool that examines bytecode to detect software bugs and has already been used in
research~\cite{AP10, HP07, HP04}. Specifically, we ran FindBugs on all the project
versions of all the projects that exist in the Maven\footnote{\url{http://maven.apache.org/}}
repository (approximately 265GB of data). Then we observed the changes that
involved the security bugs and their characteristics. This research builds upon
our earlier work on the topic~\cite{MGS12}.

@@

@@

\bibliographystyle{IEEEtran}
\bibliography{msr}

>>>>

One of the most common approaches to identify security bugs is
{\it static analysis}~\cite{CW07}. This kind of analysis involves the
inspection of the program's source or object code without executing
it. For our research we used {\it FindBugs},\footnote{\url{http://findbugs.sourceforge.net/}}
a static analysis tool that examines bytecode to detect software bugs and has already been used in
research~\cite{AP10, HP07, HP04, HW08}. Specifically, we ran FindBugs on all the project
versions of all the projects that exist in the Maven\footnote{\url{http://maven.apache.org/}}
repository (approximately 265GB of data). Then we observed the changes that
involved the security bugs and their characteristics. This research builds upon
our earlier work on the topic~\cite{MGS12}.

@@

%\begin{figure}
%	\includegraphics{arch.pdf}
%\end{figure}

@@

\bibliographystyle{IEEEtran}
\bibliography{evol}
